%% Acknowledgements.
\chapter*{Acknowledgements}

\begin{CJK*}{UTF8}{goth}
\noindent 山より海の方が好きです
\end{CJK*}

\vspace{0.3cm}

\noindent Some may compare research to trekking up a mountain: walking through challenges to reach a summit. My Ph.D. journey, however, feels more like voyaging across the ocean: exploring the vast unknown to expand horizons.

\vspace{0.3cm}

\noindent Although thrilled and enthusiastic about studying in a different country, my journey set sail during the COVID-19 pandemic. Spending the first two weeks isolated in my accommodation cast a shadow and added some anxiety to the voyage ahead. The pandemic was both a challenge and an opportunity: thanks to Sumi's insightful revisions and the collaboration with medical practitioners, my first research paper was published near the end of the first year.

\vspace{0.3cm}

\noindent Sailing into the second year, I'd like to thank Syed's support on the robotic project we collaborated on. Meanwhile, as the pandemic faded away, I witnessed how the written history was "fine-tuned" to alter how people perceived the world. Upholding scientific integrity is as crucial as maintaining faithfulness to history. I want to thank my earnest friend Dongya for standing by and helping me sail out of the looming storm from the cunning authority, which marked a turning point in my journey. 

\vspace{0.3cm}

\noindent Guided by my new supervisors, Johan and Sareh, the third year marked a new chapter after the storm. Thanks to their continuous support, we added three more publications by the end of my Ph.D. journey. Additionally, I want to thank the Alan Turing Institute for the opportunity to participate in the Data Study Group, where I met TJ, Leo, Deepak, Mellie, Hanz, Paul, and others who navigated through different paths and revealed distinct aspects of machine learning to me.

\vspace{0.3cm}

\noindent My journey of research will continue. More valuable than buried treasure or research discovery is the courage to keep sailing without being apprehensive about the future.

\vspace{0.5cm}

\raggedleft
{\normalsize \textup{Han Wu}\\ May, 2024}

\justifying
