\chapter*{List of Publications}

\noindent \textbf{H. Wu}, W. Ruan, J. Wang, D. Zheng, B. Liu, Y. Geng, X. Chai, J. Chen, K. Li, S. Li, S. Helal, "Interpretable Machine Learning for COVID-19: An Empirical Study on Severity Prediction Task", in IEEE Transactions on Artificial Intelligence, vol. 4, no. 4, pp. 764-777. 2021.

\vspace{4pt}

\noindent
H. Liu, J. Wang, Y. Geng, K. Li, \textbf{H. Wu}, J. Chen, X. Chai, S. Li, D. Zheng, "Fine-Grained Assessment of COVID-19 Severity Based on Clinico-Radiological Data Using Machine Learning", in International Journal of Environmental Research and Public Health, vol. 19, no. 17, pp. 10665. 2022.

\vspace{4pt}

\noindent
\textbf{H. Wu}, S. Yunas, S. Rowlands, W. Ruan and J. Wahlström, "Adversarial Driving: Attacking End-to-End Autonomous Driving", in IEEE Intelligent Vehicles Symposium (IV), Anchorage, USA. 2023.

\vspace{4pt}

\noindent
\textbf{H. Wu}, S. Yunas, S. Rowlands, W. Ruan and J. Wahlström, "Adversarial Detection: Attacking Object Detection in Real Time", in IEEE Intelligent Vehicles Symposium (IV), Anchorage, USA. 2023.

\vspace{4pt}

\noindent
\textbf{H. Wu}, S. Rowlands, and J. Wahlström. "A Man-in-the-Middle Attack against Object Detection Systems". (Minor Revision)

\vspace{4pt}

\noindent
\textbf{H. Wu}, S. Rowlands, and J. Wahlström. "Distributed Black-box Attack against Image Classification Cloud Services". (Major Revision)

% [6] Adversarial Tracking: Attacking 3D Multi-Object Tracking in Real Time.

% [7] Adversarial Patch: Physical Patch in Carla Simulator.
